### 2021-07-31 acknowledgement.tex
text in italic

\section*{\hfill \Huge Acknowledgement \hfill}%
\label{sec:Acknowledgement}

@@

I take this opportunity to express profound sense of gratitude and respect to
all those who helped me throughout the duration of this project.

@@

First and foremost, I would like to thank my supervisor of this project, Prof.
\textbf{Kajari Bhattacharjee}, for her valuable time and guidance. Her
willingness to motivate me has contributed tremendously to my project.

@@

I would also like to thank Prof. \textbf{Srijeeta Chakrabarti}, Head of
Department of Computer Science, for providing with a good environment and
facilities to work on this project.

@@

I regret any inadvertent omissions.

>>>>

\section*{}%

\begin{center}
	{
		\Huge
		\textbf{Acknowledgement}
	}
\end{center}

@@

\textit{
	I take this opportunity to express profound sense of gratitude and respect to
	all those who helped me throughout the duration of this project.
}

@@

\textit{
	First and foremost, I would like to thank my supervisor of this project, Prof.
	\textbf{Kajari Bhattacharjee}, for her valuable time and guidance. Her
	willingness to motivate me has contributed tremendously to my project.
}

@@

\textit{
	I would also like to thank Prof. \textbf{Srijeeta Chakrabarti}, Head of
	Department of Computer Science, for providing with a good environment and
	facilities to work on this project.
}

@@

\textit{
	I regret any inadvertent omissions.
}
